\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{tocloft}

% Page style
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Rikugan SRS}
\fancyhead[R]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% Hyperref setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Rikugan - Software Requirements Specification},
    pdfpagemode=FullScreen,
}

% Code listings setup
\lstset{
    basicstyle=\ttfamily\small,
    breaklines=true,
    frame=single,
    backgroundcolor=\color{gray!10},
    keywordstyle=\color{blue},
    commentstyle=\color{green!60!black},
    stringstyle=\color{red}
}

\title{
    \vspace{2cm}
    \Huge \textbf{Software Requirements Specification}\\
    \vspace{0.5cm}
    \LARGE for\\
    \vspace{0.5cm}
    \Huge \textbf{Rikugan}\\
    \vspace{0.3cm}
    \Large A Bounty-Based Project Management System\\
    \vspace{2cm}
}

\author{
    Version 1.0\\
    \vspace{0.5cm}
    Prepared by CSCI3100 Development Team\\
    \vspace{0.3cm}
    \today
}

\date{}

\begin{document}

\maketitle
\newpage

\tableofcontents
\newpage

\section{Introduction}

\subsection{Purpose}
This SRS document specifies requirements for Rikugan v1.0, a bounty-based project management web application combining Kanban functionality with gamified task assignment and rewards. It covers user authentication, task management, role-based access control, and reward tracking.

\subsection{Document Conventions}
\textbf{Bold text} indicates system components; \textit{italic text} represents actions/responses; \texttt{monospace} denotes technical elements. Requirements use REQ-XX format. Priority levels: High (essential), Medium (important), Low (nice-to-have).

\subsection{Product Scope}
Rikugan is a web-based project management system using gamification and role-based task assignment. It provides task visibility through Kanban boards, developer motivation via bounty rewards, and structured role hierarchies (Goons, Hashira, Oyakatasama) for accountability and collaboration.

\subsection{References}
IEEE Std 830-1998; React, Vite, HeroUI, MySQL, and Docker documentation available at respective official websites.

\newpage
\section{Overall Description}
\label{sec:overall-description}

\subsection{Product Perspective}
Rikugan is a self-contained web application for project management with gamification via a bounty-based reward system. Architecture: React/Vite frontend, Node.js backend, MySQL database, Docker containerization.

\subsection{Product Functions}
\begin{itemize}
    \item \textbf{Authentication}: Secure login, role-based access control, team license validation
    \item \textbf{Task Management}: Bounty creation, Kanban boards, status tracking, deadline penalties
    \item \textbf{User Management}: Profiles, earnings tracking, performance monitoring
    \item \textbf{Notifications}: Task assignments, deadline reminders, achievements
    \item \textbf{Analytics}: Task statistics, performance metrics, progress visualization
\end{itemize}

\subsection{User Classes and Characteristics}
\begin{itemize}
    \item \textbf{Goons}: Entry-level programmers; task selection, status updates, profile viewing; basic permissions
    \item \textbf{Hashira}: Senior programmers; all Goon functions plus task creation and team monitoring; elevated permissions
    \item \textbf{Oyakatasama}: Administrators; full system access including user management and configuration; admin privileges
\end{itemize}

\subsection{Operating Environment}
\textbf{Client}: Modern browsers (Chrome 90+, Firefox 88+, Safari 14+, Edge 90+), JavaScript enabled, 1024x768 min resolution.  
\textbf{Server}: Node.js v16+, MySQL 8.0+, Docker, Ubuntu 20.04 LTS, 4GB RAM, 20GB storage.  
\textbf{Development}: React 18+, Vite, HeroUI, ES2020+.

\subsection{Design and Implementation Constraints}
\textbf{Technical}: React/Vite web app, MySQL database, Docker containers, HeroUI components.  
\textbf{Policy}: Secure authentication, basic privacy protection.  
\textbf{Resources}: One-month timeline, 5-person student team, educational project, development environment only.  
\textbf{Interface}: Responsive design for desktop/tablet, basic accessibility compliance.

\subsection{Assumptions and Dependencies}
\textbf{Assumptions}: Users familiar with web apps, team has development tools, MySQL/Docker properly configured.  
\textbf{Dependencies}: React, HeroUI, MySQL, Docker, Node.js, Vite.  
\textbf{Risks}: Learning curve, Docker setup complexity, time constraints, library compatibility.

\newpage
\section{System Features}
\label{sec:system-features}

\subsection{User Authentication and Authorization}
\textbf{Priority: High} - Essential for security and role-based access control.

\paragraph{REQ-1: User Registration} Oyakatasama can create accounts with username (3-50 chars), email, password (8+ chars), and role.

\paragraph{REQ-2: User Login} Authenticate via username/email and password; 8-hour session timeout.

\paragraph{REQ-3: Role-Based Access}  
\textbf{Goons}: Task selection, status updates, profile viewing.  
\textbf{Hashira}: All Goon functions plus task creation and team monitoring.  
\textbf{Oyakatasama}: All functions plus user/system administration.

\paragraph{REQ-4: License Management} Hard-coded team license key via environment config; invalid license blocks all access.

\subsection{Task Management System}
\textbf{Priority: High} - Core project management functionality.

\paragraph{REQ-5: Task Creation} Hashira create tasks with name (max 100 chars), description (max 1000 chars), bounty amount (positive), deadline (future date), priority, and skill tags.

\paragraph{REQ-6: Task Assignment} Goons select available tasks; automatic assignment to first qualified user.

\paragraph{REQ-7: Kanban Board} Display tasks in columns: Available, In Progress, Review, Completed.

\paragraph{REQ-8: Task Status Updates} Assigned users update status and add progress comments.

\paragraph{REQ-9: Deadline Management} Track deadlines; apply monetary penalties for missed deadlines.

\paragraph{REQ-10: Task Deletion} Hashira/Oyakatasama delete tasks only when Available or unassigned.

\subsection{User Profile and Reward System}
\textbf{Priority: Medium} - Gamification and engagement.

\paragraph{REQ-11: User Profile} Maintain username, email, role, balance, task history, and performance statistics.

\paragraph{REQ-12: Bounty Rewards} Auto-credit user accounts upon task completion.

\paragraph{REQ-13: Penalty System} Apply configurable penalties for missed deadlines.

\paragraph{REQ-14: Performance Tracking} Display tasks completed, avg completion time, success rate, total earnings.

\subsection{Notification System}
\textbf{Priority: Medium} - User engagement and communication.

\paragraph{REQ-15: Task Notifications} Notify on: task assignment, 24hr deadline reminders, status updates, completion/cancellation.

\paragraph{REQ-16: Achievement Notifications} Notify on: first task completion, earning milestones, performance improvements, role promotions.

\newpage
\section{Other Non-Functional Requirements}
\label{sec:nonfunctional}

\subsection{Performance Requirements}
\begin{itemize}
    \item Page load: <3s; API response: 95\% <500ms; Database queries: <2s; Login: <1s
    \item Support 50 concurrent users, 100 task updates/min, notifications within 5s
    \item Capacity: 200 users, 1000 active tasks
    \item Frontend <100MB RAM/tab, DB <1GB, server CPU <70\%
\end{itemize}

\subsection{Security Requirements}
\begin{itemize}
    \item \textbf{Authentication}: 8+ char passwords, bcrypt hashing, JWT tokens, role-based access, secure logout
    \item \textbf{Data Security}: HTTPS, encrypted credentials, parameterized queries, input sanitization, XSS prevention
    \item \textbf{System}: Rate limiting, security logging, no sensitive info in errors
\end{itemize}

\subsection{Software Quality Attributes}
\begin{itemize}
    \item \textbf{Usability}: Intuitive interface, consistent navigation, clear errors, responsive design, WCAG 2.1 Level A
    \item \textbf{Reliability}: 95\% uptime, graceful degradation, automatic error recovery, data consistency
    \item \textbf{Maintainability}: Modular React code, API docs, separation of concerns, ESLint standards, 70\% test coverage
    \item \textbf{Portability}: Cross-browser (Chrome/Firefox/Safari/Edge), Docker containers
    \item \textbf{Testability}: Unit testing, automated API testing, test data procedures
\end{itemize}

\subsection{Business Rules}
\begin{itemize}
    \item \textbf{User Roles}: Only Oyakatasama manage accounts; Hashira/Oyakatasama create tasks; Goons/Hashira work on tasks; users update only assigned tasks
    \item \textbf{Tasks}: One user per task, positive bounties, future deadlines, completed tasks immutable, status flow: Available → In Progress → Review → Completed
    \item \textbf{Financial}: Auto bounty payment on completion, auto penalties on missed deadlines, -\$100 balance minimum, all transactions logged, admin-only manual adjustments
    \item \textbf{License}: One hard-coded key per team via environment config; invalid license blocks all access
    \item \textbf{Notifications}: 24hr deadline reminders, immediate assignment alerts, milestone achievements, admin priority
\end{itemize}

\newpage
\section{Other Requirements}
\label{sec:other-requirements}

\subsection{Database Requirements}
MySQL 8.0+, InnoDB, UTF-8, daily backups. Core tables: users (id, username, email, password\_hash, role, balance, timestamps), tasks (id, title, description, bounty\_amount, deadline, status, created\_by, assigned\_to, timestamps), notifications (id, user\_id, type, message, read\_status, created\_at), licenses (id, license\_key, expiry\_date, status, max\_users, created\_at). Indexes on user\_id, task\_status, created\_at.

\subsection{Development Environment}
Docker 20.0+ with compose, Node.js 16+, npm/yarn, Git, Vite build, hot reload, environment config (.env), automated testing.

\subsection{Legal and Compliance}
Educational use only, no commercial transactions, university policy compliance, open source libraries, MIT license. Privacy: minimal data collection (username/email), local environment only, user consent, data deletion on account termination.

\subsection{Testing Requirements}
Jest for unit tests, 70\% coverage for critical logic, API endpoint testing, React component integration testing, E2E for critical workflows. Test database with seed data, cleanup procedures.

\end{document}
