\documentclass[12pt]{article}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{margin=1in}

\title{User Manual for Rikugan Frontend Web Application}
\author{Rikugan Team}
\date{\today}

\begin{document}

\maketitle

\tableofcontents

\section{Introduction}
This manual provides instructions for end users of the Rikugan frontend web application. The application is designed for team management, task assignment, notifications, and user profile management.

\section{Getting Started}
\subsection{Accessing the Website}
Open your web browser and navigate to the deployed URL or run the application locally using the provided instructions in the README.

\subsection{User Roles and Account Creation}
The system supports three user roles with different permissions:
\begin{itemize}
  \item \textbf{Oyakatasama (Admin):} Full system access, creates teams and manages all users
  \item \textbf{Hashira (Senior):} Can create tasks and manage team members
  \item \textbf{Goon (Junior):} Can work on tasks and earn bounties
\end{itemize}

\subsection{First-Time Setup (For Oyakatasama/Admin)}
If you are the team administrator:
\begin{enumerate}
  \item On the welcome page, click \textbf{"Join the Corps"} to create a new admin account
  \item Fill in your registration details:
  \begin{itemize}
    \item Username
    \item Email address
    \item Password
    \item Select role: \textbf{Oyakatasama}
  \end{itemize}
  \item After registration, you will be directed to the \textbf{Team Creation} page
  \item Enter your team information:
  \begin{itemize}
    \item Team Name
    \item Team Description
    \item \textbf{License Key} - Use one of the default licenses from the system configuration:
    \begin{itemize}
      \item \texttt{RIKUGAN-2024-TEAM-A} (50 users, expires 2025-12-31)
      \item \texttt{RIKUGAN-2024-TEAM-B} (100 users, expires 2025-12-31)
      \item \texttt{RIKUGAN-2024-TEAM-C} (25 users, expires 2026-06-30)
      \item \texttt{DSCPMS-2024-UNLIMITED-ACCESS} (demo/development)
    \end{itemize}
  \end{itemize}
  \item Click \textbf{Create Team} to complete setup
  \item You can now add team members (Hashira and Goons) from the Team Management page
\end{enumerate}

\subsection{Adding Team Members (For Oyakatasama)}
After creating your team:
\begin{enumerate}
  \item Navigate to \textbf{Team Management} from the sidebar
  \item Click \textbf{Add Member} or \textbf{Create User Account}
  \item Fill in the new member's details:
  \begin{itemize}
    \item Username
    \item Email address
    \item Temporary password (share this with the user securely)
    \item Select role: Hashira or Goon
  \end{itemize}
  \item Click \textbf{Create Account}
  \item Share the login credentials with the new user
\end{enumerate}

\subsection{Login (For Hashira and Goons)}
If an admin has created an account for you:
\begin{enumerate}
  \item On the welcome page, click \textbf{"Login"}
  \item Enter the credentials provided by your admin:
  \begin{itemize}
    \item Email or Username
    \item Password
  \end{itemize}
  \item Click \textbf{Login}
  \item You will be directed to the dashboard
  \item \textbf{Important:} Change your password immediately after first login for security
\end{enumerate}

\section{Main Features}

\subsection{Sidebar Navigation}
The sidebar provides quick access to all main sections:
\begin{itemize}
  \item Dashboard
  \item Team Management
  \item Task Management
  \item Notifications
  \item Profile
  \item Theme Toggle (Light/Dark)
  \item Logout
\end{itemize}

\subsection{Dashboard}
\begin{itemize}
  \item View an overview of your team, tasks, and recent activity.
  \item Access quick links to other sections.
\end{itemize}

\subsection{Team Management}
\begin{itemize}
  \item View your current team, its members, and license status.
  \item \textbf{For Oyakatasama:} Create accounts for new team members (Hashira or Goons):
  \begin{itemize}
    \item Click \textbf{Add Member}
    \item Enter username, email, password, and select role
    \item New user can login immediately with the provided credentials
  \end{itemize}
  \item View team member details including roles and permissions.
  \item Remove team members if needed (admin permission required).
  \item Edit team information such as name and description.
  \item Monitor team license status and expiration date.
  \item Deactivate the team if necessary (admin only).
\end{itemize}

\subsection{Task Management}
\subsubsection{Creating Tasks (For Hashira and Oyakatasama)}
\begin{itemize}
  \item Navigate to \textbf{Task Management} from the sidebar
  \item Click \textbf{Create Task}
  \item Fill in task details:
  \begin{itemize}
    \item Task title
    \item Description
    \item Priority (Low, Medium, High)
    \item Deadline
    \item Bounty amount (reward for completion)
  \end{itemize}
  \item Click \textbf{Create} to publish the task
  \item Task will appear in the taskboard as \textbf{Available}
\end{itemize}

\subsubsection{Accepting Tasks (For All Users)}
\begin{itemize}
  \item Navigate to \textbf{Taskboard} from the sidebar
  \item Browse available tasks in the board
  \item Click on a task card to view details
  \item Click \textbf{Accept Task} or \textbf{Assign to Self}
  \item Task status changes to \textbf{In Progress}
  \item Task moves to your \textbf{Taken Task} tab
\end{itemize}

\subsubsection{Completing Tasks (For Task Assignee)}
\begin{itemize}
  \item Navigate to \textbf{Taskboard} from the sidebar
  \item Go to the \textbf{Taken Task} tab
  \item Find your in-progress task
  \item Complete the work as described in the task
  \item Click \textbf{Complete Task} or \textbf{Submit for Review}
  \item Task status changes to \textbf{Under Review}
  \item Wait for the task creator to review your work
\end{itemize}

\subsubsection{Reviewing Tasks (For Task Creator)}
\begin{itemize}
  \item Navigate to \textbf{Task Management} or \textbf{Taskboard}
  \item View tasks with status \textbf{Under Review}
  \item Review the completed work
  \item Click \textbf{Mark as Completed} to approve the task
  \item The task assignee will receive:
  \begin{itemize}
    \item A notification of task completion
    \item Bounty payment added to their balance
  \end{itemize}
\end{itemize}

\subsubsection{Viewing Updated Balance}
\begin{itemize}
  \item After a task is approved, your balance will be updated with the bounty amount
  \item Check the notification panel for confirmation
  \item View your updated balance in the dashboard or profile
  \item \textbf{Note:} If your balance is not immediately updated, refresh the page to see the changes
\end{itemize}

\subsubsection{Task Workflow Summary}
\begin{enumerate}
  \item Hashira/Oyakatasama creates task → Task appears as \textbf{Available}
  \item Any user accepts task → Task becomes \textbf{In Progress}
  \item User completes work and submits → Task goes to \textbf{Under Review}
  \item Task creator reviews and approves → Task marked as \textbf{Completed}
  \item User receives notification and bounty payment → Balance updated
\end{enumerate}

\subsection{Notifications}
\begin{itemize}
  \item View all notifications related to your account and team.
  \item Common notification types:
  \begin{itemize}
    \item Task assigned to you
    \item Task submitted for review (for task creators)
    \item Task completed and approved
    \item Bounty payment received
    \item Deadline reminders
    \item Team updates
  \end{itemize}
  \item Filter notifications by unread status.
  \item Mark notifications as read or delete them.
  \item Use the search bar to find specific notifications.
  \item Click on a notification to view details or navigate to the related task.
\end{itemize}

\subsection{User Profile}
\begin{itemize}
  \item Click your avatar or username in the sidebar to view and edit your profile.
  \item Update your email and other personal information.
  \item \textbf{Change Password:} For security, change your password after first login:
  \begin{itemize}
    \item Navigate to Profile Settings
    \item Click \textbf{Change Password}
    \item Enter your old password and new password
    \item Confirm the new password
  \end{itemize}
  \item View your account statistics including tasks completed and bounties earned.
\end{itemize}

\subsection{Theme Toggle}
Switch between light and dark mode using the theme toggle button in the sidebar.

\subsection{Logout}
Click the Logout button in the sidebar to securely sign out of your account.

\section{Tips and Troubleshooting}
\begin{itemize}
  \item For best experience, use a modern web browser (Chrome, Firefox, Edge).
  \item \textbf{First Login:} Always change your password after receiving credentials from an admin.
  \item \textbf{License Issues:} If you cannot access features, verify that your team has a valid license.
  \item \textbf{Forgot Password:} Contact your team administrator (Oyakatasama) to reset your password.
  \item \textbf{Cannot Create Team:} Ensure you have a valid license key from the system administrator.
  \item \textbf{Balance Not Updated:} After completing a task, refresh the page if your balance doesn't update immediately.
  \item \textbf{Task Not Appearing:} Check the correct tab (Available, Taken Task, or Completed) in the taskboard.
  \item \textbf{Cannot Accept Task:} Ensure you have sufficient permissions and your team has a valid license.
  \item If you encounter issues, try refreshing the page or clearing your browser cache.
  \item For further help, contact your system administrator or support team.
\end{itemize}

\section{Security Best Practices}
\begin{itemize}
  \item Change the default password provided by your admin immediately after first login.
  \item Use a strong password with at least 8 characters, including uppercase, lowercase, numbers, and special characters.
  \item Do not share your login credentials with others.
  \item Always logout when finished using the application.
  \item Report any suspicious activity to your team administrator.
\end{itemize}

\section{Contact and Support}
For questions or support, refer to the README or contact the Rikugan development team.

\end{document}
