\documentclass[12pt]{article}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{margin=0.8in}

\title{Rikugan Frontend Web Application\\User Manual v1.0.0}
\author{Rikugan Team}
\date{December 22, 2025}

\begin{document}

\maketitle

\section*{Release Notes - Version 1.0.0}
\subsection*{Release Date: December 22, 2025}

\textbf{Initial Release Features:}
\begin{itemize}[noitemsep]
  \item User authentication system with role-based access control (Oyakatasama, Hashira, Goon)
  \item Team creation and management with license validation
  \item Task management system with bounty rewards
  \item Kanban-style taskboard with task assignment workflow
  \item Real-time notification system
  \item User profile management with statistics
  \item Light/Dark theme support
  \item Transaction history and balance tracking
\end{itemize}

\textbf{Known Limitations:}
\begin{itemize}[noitemsep]
  \item Balance updates may require page refresh
  \item Password reset requires admin intervention
\end{itemize}

\tableofcontents
\newpage

\section{Introduction}
This manual provides instructions for the Rikugan web application - a gamified project management system with bounty-based rewards. The application supports team collaboration, task assignment, and user performance tracking.

\section{Getting Started}

\subsection{User Roles}
\begin{itemize}[noitemsep]
  \item \textbf{Oyakatasama (Admin):} Full system access, creates teams, manages users
  \item \textbf{Hashira (Senior):} Creates tasks, manages team members
  \item \textbf{Goon (Junior):} Completes tasks, earns bounties
\end{itemize}

\subsection{First-Time Setup (Admin)}
\begin{enumerate}[noitemsep]
  \item Click \textbf{"Join the Corps"} on welcome page
  \item Register with role: Oyakatasama
  \item Enter team details (name, description)
  \item Enter valid license key (e.g., \texttt{DSCPMS-2024-UNLIMITED-ACCESS})
  \item Create team
\end{enumerate}

\subsection{Adding Members (Admin)}
\begin{enumerate}[noitemsep]
  \item Go to \textbf{Team Management}
  \item Click \textbf{Add Member}
  \item Enter: username, email, temporary password, role
  \item Share credentials with new user
\end{enumerate}

\subsection{Login (Hashira/Goon)}
\begin{enumerate}[noitemsep]
  \item Click \textbf{"Login"} on welcome page
  \item Enter credentials from admin
  \item Change password immediately after first login
\end{enumerate}

\section{Core Features}

\subsection{Dashboard}
View team overview, task statistics, and recent activity. Access quick links to other sections.

\subsection{Task Workflow}

\textbf{1. Creating Tasks (Hashira/Admin):}
\begin{itemize}[noitemsep]
  \item Navigate to Task Management
  \item Click Create Task
  \item Fill in title, description, priority, deadline, bounty amount
  \item Task appears as Available in taskboard
\end{itemize}

\textbf{2. Accepting Tasks (All Users):}
\begin{itemize}[noitemsep]
  \item Go to Taskboard
  \item Click on available task
  \item Click Accept Task
  \item Task moves to Taken Task tab with In Progress status
\end{itemize}

\textbf{3. Completing Tasks:}
\begin{itemize}[noitemsep]
  \item Open Taken Task tab
  \item Complete the work
  \item Click Submit for Review
  \item Task status: Under Review
\end{itemize}

\textbf{4. Reviewing Tasks (Creator):}
\begin{itemize}[noitemsep]
  \item View tasks Under Review
  \item Click Mark as Completed
  \item Assignee receives notification and bounty payment
  \item \textit{Note: Refresh page if balance doesn't update immediately}
\end{itemize}

\subsection{Team Management}
\begin{itemize}[noitemsep]
  \item View team members, roles, and license status
  \item Admin: Create user accounts, remove members, edit team details
  \item Monitor team statistics and performance
\end{itemize}

\subsection{Notifications}
\begin{itemize}[noitemsep]
  \item Task assignments, completions, bounty payments
  \item Deadline reminders and team updates
  \item Filter by unread, search, mark as read, or delete
\end{itemize}

\subsection{User Profile}
\begin{itemize}[noitemsep]
  \item View/edit personal information
  \item Change password (required after first login)
  \item View task completion statistics and earnings
\end{itemize}

\section{Tips and Troubleshooting}
\begin{itemize}
  \item For best experience, use a modern web browser (Chrome, Firefox, Edge).
  \item \textbf{First Login:} Always change your password after receiving credentials from an admin.
  \item \textbf{License Issues:} If you cannot access features, verify that your team has a valid license.
  \item \textbf{Forgot Password:} Contact your team administrator (Oyakatasama) to reset your password.
  \item \textbf{Cannot Create Team:} Ensure you have a valid license key from the system administrator.
  \item \textbf{Balance Not Updated:} After completing a task, refresh the page if your balance doesn't update immediately.
  \item \textbf{Task Not Appearing:} Check the correct tab (Available, Taken Task, or Completed) in the taskboard.
  \item \textbf{Cannot Accept Task:} Ensure you have sufficient permissions and your team has a valid license.
  \item If you encounter issues, try refreshing the page or clearing your browser cache.
  \item For further help, contact your system administrator or support team.
\end{itemize}

\section{Security Best Practices}
\begin{itemize}
  \item Change the default password provided by your admin immediately after first login.
  \item Use a strong password with at least 8 characters, including uppercase, lowercase, numbers, and special characters.
  \item Do not share your login credentials with others.
  \item Always logout when finished using the application.
  \item Report any suspicious activity to your team administrator.
\end{itemize}

\section{Contact and Support}
For questions or support, refer to the README or contact the Rikugan development team.

\end{document}
Quick Reference}

\subsection{Sidebar Navigation}
Dashboard | Taskboard | Task Management (Hashira/Admin) | Notifications | Team Management (Admin) | Profile | Theme Toggle | Logout

\subsection{Available License Keys}
\begin{itemize}[noitemsep]
  \item \texttt{RIKUGAN-2024-TEAM-A} (50 users, expires 2025-12-31)
  \item \texttt{RIKUGAN-2024-TEAM-B} (100 users, expires 2025-12-31)
  \item \texttt{DSCPMS-2024-UNLIMITED-ACCESS} (demo/development)
\end{itemize}

\section{Troubleshooting}

\begin{itemize}[noitemsep]
  \item \textbf{Balance not updated:} Refresh the page
  \item \textbf{Cannot accept task:} Check team license validity
  \item \textbf{Forgot password:} Contact admin (Oyakatasama)
  \item \textbf{Task not appearing:} Check correct tab (Available/Taken/Completed)
  \item Use modern browsers: Chrome, Firefox, Edge
  \item Clear browser cache if experiencing issues
\end{itemize}

\section{Security}

\begin{itemize}[noitemsep]
  \item Change default password immediately after first login
  \item Use strong passwords (8+ characters, mixed case, numbers, symbols)
  \item Never share login credentials
  \item Always logout when finished
  \item Report suspicious activity to admin
\end{itemize}

\vspace{1em}
\noindent\textbf{For detailed documentation:} See API\_DOCUMENTATION.md and DEPLOYMENT.md\\
\textbf{Support:} Contact Rikugan development team or system administrator